Value-Suppressing Uncertainty Maps

### 2017-09-17 paper/figures.tex
Updated virus example, made more JH edits.

\newcommand{\taskTwoQuartiles}{
	\begin{figure}
		\centering
		\includegraphics[width=0.75\columnwidth]{exp2histogram.pdf}
		\caption{A histogram of the distribution of uncertainty across all participants guesses from the prediction experiment. While participants generally favored low uncertainty in guesses, our stimuli design encouraged them to make at least some guesses with higher uncertainty. VSUPs encouraged more guesses with middling uncertainty, and discouraged highly uncertain guesses.}
		\label{fig:taskTwoQuartiles}
	\end{figure}
}
%\newcommand{\performanceFig}{
%	\begin{figure}[t]
%		\centering
%		\includegraphics[width=0.9\columnwidth]{performance.pdf}
%		\caption{
%			The number of discrete color categories in traditional bivariate color maps versus VSUPs, assuming value is encoded by the Viridis color map~\protect\cite{viridis}, and uncertainty is encoded by saturation/value (whiter values are more uncertain). Since these whiter uncertain colors are closer together in CIELAB space, and VSUPs intentionally require fewer color bins in those regions, VSUPs always have more color categories than the corresponding 2D bivariate map. The red lines denote:
%		  \textbf{1)} Theoretical 50\% JND from CIELAB specification.
%			\textbf{2)} 50\% JND from controlled lab study of Mahy et al.~\protect\cite{mahy1994evaluation}.
%			\textbf{3)} 50\% JND from Szafir et al.\protect\cite{szafir2014adapting}.
%			\textbf{4)} 50\% JND for small visual targets from Stone et al.~\protect\cite{stone2014engineering}.
%			\textbf{5)} The threshold resulting in the simplest possible (2x2) bivariate map.
%	    }
%		\label{fig:performance}
%	\end{figure}
%}

@@

	\centering
	\includegraphics[width=\columnwidth]{viral-vsum.pdf}
	\vspace{-15px}
	\caption{Variability for 12 different viral populations of SIV, encoded with a VSUP. The magnitude of mutation rate, as well as the generally poorer quality of data towards the end of the sequence, is more readily visible than with the traditional bivariate color map. }
	\label{fig:viralVsum}
\end{figure}
}

>>>>

\newcommand{\taskTwoQuartiles}{
	\begin{figure}
		\centering
		\includegraphics[width=0.75\columnwidth]{exp2histogram.pdf}
		\caption{A histogram of the distribution of uncertainty across all participants guesses from the prediction experiment. For each trial, participants made 5 guesses. While participants generally favored low uncertainty in guesses, our stimuli design encouraged them to make at least some guesses with higher uncertainty. VSUPs encouraged more guesses with middling uncertainty, and discouraged highly uncertain guesses.}
		\label{fig:taskTwoQuartiles}
	\end{figure}
}
%\newcommand{\performanceFig}{
%	\begin{figure}[t]
%		\centering
%		\includegraphics[width=0.9\columnwidth]{performance.pdf}
%		\caption{
%			The number of discrete color categories in traditional bivariate color maps versus VSUPs, assuming value is encoded by the Viridis color map~\protect\cite{viridis}, and uncertainty is encoded by saturation/value (whiter values are more uncertain). Since these whiter uncertain colors are closer together in CIELAB space, and VSUPs intentionally require fewer color bins in those regions, VSUPs always have more color categories than the corresponding 2D bivariate map. The red lines denote:
%		  \textbf{1)} Theoretical 50\% JND from CIELAB specification.
%			\textbf{2)} 50\% JND from controlled lab study of Mahy et al.~\protect\cite{mahy1994evaluation}.
%			\textbf{3)} 50\% JND from Szafir et al.\protect\cite{szafir2014adapting}.
%			\textbf{4)} 50\% JND for small visual targets from Stone et al.~\protect\cite{stone2014engineering}.
%			\textbf{5)} The threshold resulting in the simplest possible (2x2) bivariate map.
%	    }
%		\label{fig:performance}
%	\end{figure}
%}

@@

	\centering
	\includegraphics[width=\columnwidth]{viral-vsum.pdf}
	\vspace{-15px}
	\caption{Variability for 12 different viral populations of SIV, encoded with a VSUP. By suppressing uncertain information, the VSUP version removes the apparent spike in value at the second column, which is an artifact of sampling error due to poor coverage in that region. It also suppresses apparent inter-species variability in the solid orange spike at location ~9,500, which, again, is a function of poor coverage rather than a genuine per-strain difference.  }
	\label{fig:viralVsum}
\end{figure}
}
